Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Updated Figure 5

nldr_two_curvy_original + 
  trimesh_two_curvy_removed1_umap_with_data +
  two_curvy_proj_umap_first_model1 +
  two_curvy_proj_umap_all_model1 +
  plot_layout(ncol = 2)
```

>>>>

nldr_two_curvy_original + 
  trimesh_two_curvy_removed1_umap_with_data +
  two_curvy_proj_umap_first_model1 +
  two_curvy_proj_umap_all_model1 +
  plot_layout(ncol = 2, heights = c(1, 2))
```
